\documentclass{supervision}
\usepackage{course}
\usepackage{code}

\Supervision{3}

\begin{document}
\begin{questions}
  \question A C programmer is working with a little-endian machine with $8$
    bits in a byte and $4$ bytes in a word. The compiler supports unaligned
    access and uses $1$, $2$ and $4$ bytes to store \lstinline|char|,
    \lstinline|short| and \lstinline|int| respectively. The programmer writes
    the following definitions (code as written below) to access values in main
    memory (in the table below):

    \begin{cpp}[gobble=6]
      // Address | Byte offset
      // ....... | 00 01 02 03
      // ________|_____________
      // 0x04 .. | 10 00 00 00
      // 0x08 .. | 61 72 62 33
      // 0x0c .. | 33 00 00 00
      // 0x10 .. | 78 0c 00 00
      // 0x14 .. | 08 00 00 00
      // 0x18 .. | 01 00 4c 03
      // 0x1c .. | 18 00 00 00

      int **i=(int **)0x04;
      short **pps=(short **)0x1c;
      struct i2c {int i; char *c;}*p=(struct i2c*)0x10;
    \end{cpp}

    \begin{parts}
      \part[8] Write down the values for the following C expressions:
        \begin{subparts}
          \subpart \lstinline|**i|
            % This is wrong (didn't read the question properly!). 
            %
            % \begin{solution}
            %   $i$ is initialised as a double pointer to an int by casting the
            %   integer \lstinline|0x04| to an int double pointer. This means
            %   that $i$ points to memory address \lstinline|0x04|. When trying
            %   to dereference it, a memory access violation will likely occur
            %   (causing a segmentation fault) since \lstinline|0x04| is an
            %   arbitrary address. If no memory access violation occurs during
            %   each of the two dereferences then the result will be garbage.
            % \end{solution}
            \begin{solution}
              $i$ is initialised as a double pointer to an \lstinline|int| by 
              casting \lstinline|0x04| to an integer double pointer. When this 
              is double dereferenced the value stored in \lstinline|0x04| is 
              interpreted as a memory address (\lstinline|0x10|) and then the 
              int is read from there. Since this is a little-endian machine and 
              4 bytes are used to store an int the resulting integer is 
              \lstinline|0x00000c78| ($3192$).
            \end{solution}
          \subpart \lstinline|p->c[2]|
            \begin{solution}
              \lstinline|0x00|
            \end{solution}
          \subpart \lstinline|&(*pps)[1]|
            \begin{solution}

            \end{solution}
          \subpart \lstinline|++p->i|
        \end{subparts}

      \part[4] Explain why the code shown below, when executed, will print the
        value $420$.
        \begin{cpp}]gobble=8]
          #include<stdio.h>

          #define init_employee(X,Y) {(X),(Y),wage_emp}
          typedef struct Employee Em;
          struct Employee {
          int hours,salary;
          int (*wage)(Em*);
          };

          int wage_emp(Em *ths) {
          return ths->hours*ths->salary;
          }

          #define init_manager(X,Y,Z) {(X),(Y),wage_man,(Z)}
          typedef struct Manager Mn;
          struct Manager {
          int hours,salary;
          int (*wage)(Mn*);
          int bonus;
          };
          int wage_man(Mn *ths){
          return ths->hours*ths->salary+ths->bonus;
          }

          int main(void) {
          Mn m = init_manager(40,10,20);
          Em *e= (Em *) &m;
          printf("%d\n",e->wage(e));
          return 0;
          }
        \end{cpp}

      \part[8] Rewrite the C code shown in \emph{part (b)} using C++ primitives
        and give four reasons why your C++ solution is better than the C one.
    \end{parts}

  \question Rewrite your \lstinline|Matrix| class to use templates to determine
    the dimensions. You should implement functions for $+$,$-$ and $*$ making
    sure that they return matrices of the correct dimensions. Give typedef's to
    define \lstinline|Matrix| and \lstinline|Vector| as before.

  \question C++11 added rvalue references to help programmers avoid unnecessary
    copying of objects. Find out what this means and write an explanation
    including an example which demonstrates that copying has been avoided. You
    might like to start here: \url{http://www.artima.com/cppsource/rvalue.html}

    \emph{Note: that for g++ you need to pass the switch -std=c++11 to enable
    C++11 features}

\end{questions}
\end{document}
